Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-06 Final_Manuscript.Rmd
Cleaned file i-o

```{r data}
clark_measures <- read.csv("Cleaned data/clark_measures.csv")
smith <- read.csv("Cleaned data/smith.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
```

##Combining Samples

@@

Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.

@@

```{r alpha_SOO}
##SOO
#Clark
clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, 
                                          otherint_5, otherint_6, otherint_10))$total[2]
clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, 
                                          otherint_7, otherint_8, otherint_9, otherint_11, 
                                          otherint_12))$total[2]
#Smith
smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, 
                                          otherint_6, otherint_10))$total[2]
smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, 
                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
```

@@

```{r alpha_intauth}
##Interaction Authenticity
#Clark
clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, 
                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
                                           interaux_6))$total[2]
#Smith
smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, 
                                           inter_7, inter_9, inter_10, interaux_5, 
                                           interaux_6))$total[2]
```

@@

```{r alpha_SSO}
##SSO
#Clark - two items
clark_howbody_alpha<- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
#Smith - two items
smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]
#Clark - three items
clark_howbody3 <- psych::alpha(select(clark_measures, howbody_1, howbody_2, howbody_3))
#Smith - three items
smith_howbody3 <- psych::alpha(select(smith, howbody_1, howbody_2, howbody_3))
```

@@

```{r alpha_relagen}
##Relationship Agency
#Clark
clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
                                         relag_9.r))$total[2]
#Smith
smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
                                         relag_5, relag_6, relag_7, relag_8, 
                                         relag_9.r))$total[2]

#corr.test(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
#corr.test(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
##DROPPING ITEM 9
clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, 
                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]

smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, 
                                         relag_5, relag_6, relag_7, relag_8))$total[2]
```

@@

```{r alpha_career}
##Career Aspirations
#Clark
clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, 
                                             careerasp_3, careerasp4.r, careerasp_5, 
                                             careerasp_6, careerasp7.r, careerasp_8, 
                                             careerasp_9, careerasp10.r))$total[2]

#Smith
smith <- smith %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, 
                                             careerasp_3, careerasp4.r, careerasp_5, 
                                             careerasp_6, careerasp7.r, careerasp_8, 
                                             careerasp_9, careerasp10.r))$total[2]
```

@@

```{r alpha_TSO}
###TSO
#Clark--external and internal
clark_funcTSO_alpha <- psych::alpha(select(clark_measures, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
clark_physTSO_alpha <- psych::alpha(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
```

@@

@@

tally(~gender, data=clark_measures)
tally(~gender, data=smith)
```

###Description of the Samples
Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.  More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college. Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals. Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2. Due to similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined. For consistency, we limited participant data to same sex female pairs at the two colleges. These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`). The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race. There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs. The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs. `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.

# Results
```{r create_r-references, warning=FALSE, message=FALSE}
#cite_r(file = "references.bib")
r_refs(file = "r-references.bib")
```

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

@@

```{r}
# #Filtering for just one partnum and creating TSO * objectification interaction
# dyad_cswomen <- clarksmith_women %>%
#   mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
#          TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
#   filter(partnum_A==1)
# 
# 
# model <- '#####regressions 
# howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
# authenticity_A ~ d*howbody_avg_A
# howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
# authenticity_P ~ d*howbody_avg_P
# trigram_score_A ~ e1*authenticity_A
# careerasp_A ~ e2*authenticity_A
# relag_A ~ e3*authenticity_A
# trigram_score_P ~ e1*authenticity_P
# careerasp_P ~ e2*authenticity_P
# relag_P ~ e3*authenticity_P
# ######covariances
# #endogenous
# howbody_avg_A ~~ howbody_avg_P
# authenticity_A ~~ authenticity_P
# trigram_score_A ~~ trigram_score_P
# careerasp_A ~~ careerasp_P
# relag_A ~~ relag_P
# trigram_score_A ~~ 0*careerasp_A
# trigram_score_A ~~ 0*relag_A
# trigram_score_A ~~ 0*careerasp_P
# trigram_score_A ~~ 0*relag_P
# careerasp_A ~~ 0*relag_A
# careerasp_A ~~ 0*trigram_score_P
# careerasp_A ~~ 0*relag_P
# relag_A ~~ 0*trigram_score_P
# relag_A ~~ 0*careerasp_P
# trigram_score_P ~~ 0*careerasp_P
# trigram_score_P ~~ 0*relag_P
# careerasp_P ~~ 0*relag_P
# #####variances
# howbody_avg_A ~~ v1*howbody_avg_A
# howbody_avg_P ~~ v1*howbody_avg_P
# TSO_A ~~ v2*TSO_A
# TSO_P ~~ v2*TSO_P
# a2pSOO_A ~~ v3*a2pSOO_A
# a2pSOO_P ~~ v3*a2pSOO_P
# authenticity_A ~~ v4*authenticity_A
# authenticity_P ~~ v4*authenticity_P
# ##endogenous intercepts
# howbody_avg_A ~ i*1
# howbody_avg_P ~ i*1
# authenticity_A ~ i2*1
# authenticity_P ~ i2*1
# trigram_score_A ~ i3*1
# trigram_score_P ~ i4*1
# careerasp_A ~ i5*1
# careerasp_P ~ i5*1
# relag_A ~ i6*1
# relag_P ~ i6*1
# ##exogenous means
# TSO_A ~ m*1
# TSO_P ~ m*1
# a2pSOO_A ~ m2*1
# a2pSOO_P ~ m2*1
# TSO_P_SOO_A ~ m3*1
# TSO_A_SOO_P ~ m3*1
# ## exogenous covariances
# TSO_A_SOO_P ~~ c1*TSO_A
# TSO_P_SOO_A ~~ c1*TSO_P
# TSO_A_SOO_P ~~ c2*a2pSOO_P
# TSO_P_SOO_A ~~ c2*a2pSOO_A
# TSO_A ~~ c3*a2pSOO_P
# TSO_P ~~ c3*a2pSOO_A
# TSO_A ~~ c4*a2pSOO_A
# TSO_P ~~ c4*a2pSOO_P
# TSO_A_SOO_P ~~ c5*a2pSOO_A
# TSO_P_SOO_A ~~ c5*a2pSOO_P
# TSO_A_SOO_P ~~ c6*TSO_P
# TSO_P_SOO_A ~~ c6*TSO_A
# '
# 
# isatmodel <- '#####regressions 
# #Part one/two
# howbody_avg_A ~~ t*TSO_A
# howbody_avg_A ~~ a*a2pSOO_A
# howbody_avg_A ~~ b*a2pSOO_P 
# howbody_avg_A ~~ c*TSO_A_SOO_P
# 
# howbody_avg_P ~~ t*TSO_P
# howbody_avg_P ~~ a*a2pSOO_P 
# howbody_avg_P ~~ b*a2pSOO_A 
# howbody_avg_P ~~ c*TSO_P_SOO_A
# 
# TSO_A ~~ f*howbody_avg_P
# TSO_P ~~ f*howbody_avg_A
# TSO_A_SOO_P ~~ g*howbody_avg_P
# TSO_P_SOO_A ~~ g*howbody_avg_A
# 
# #Part two/three
# authenticity_A ~~ d*howbody_avg_A
# authenticity_P ~~ d*howbody_avg_P
# howbody_avg_A ~~ h*authenticity_P
# howbody_avg_P ~~ h*authenticity_A
# 
# 
# #Part three/four
# trigram_score_A ~~ e1*authenticity_A
# trigram_score_P ~~ e1*authenticity_P
# careerasp_A ~~ e2*authenticity_A
# careerasp_P ~~ e2*authenticity_P
# relag_A ~~ e3*authenticity_A
# relag_P ~~ e3*authenticity_P
# trigram_score_A ~~ e4*relag_P
# trigram_score_P ~~ e4*relag_A
# trigram_score_A ~~ e5*careerasp_P
# trigram_score_P ~~ e5*careerasp_A
# trigram_score_A ~~ e6*trigram_score_P
# #trigram_score_P ~~ e6*trigram_score_A
# careerasp_A ~~ e7*relag_P
# careerasp_P ~~ e7*relag_A
# careerasp_A ~~ e8*careerasp_P
# #careerasp_A ~~ e9*trigram_score_P
# #careerasp_P ~~ e9*trigram_score_A
# relag_A ~~ e10*relag_P
# 
# #One to three
# #direct actor effects
# authenticity_A ~~ k1*TSO_A_SOO_P
# authenticity_P ~~ k1*TSO_P_SOO_A
# authenticity_A ~~ k2*TSO_A
# authenticity_P ~~ k2*TSO_P
# authenticity_A ~~k3*a2pSOO_A
# authenticity_P ~~k3*a2pSOO_P
# 
# #direct partner effects
# authenticity_A ~~ k4*TSO_P_SOO_A
# authenticity_P ~~k4*TSO_A_SOO_P
# authenticity_A ~~ k5*TSO_P
# authenticity_P ~~ k5*TSO_A
# authenticity_A ~~ k6*a2pSOO_P
# authenticity_P ~~ k6*a2pSOO_A
# 
# #One to four
# #Direct actor effects
# trigram_score_A ~~ l1*TSO_A_SOO_P
# trigram_score_P ~~ l1*TSO_P_SOO_A
# trigram_score_A ~~ l2*TSO_A
# trigram_score_P ~~ l2*TSO_P
# trigram_score_A ~~ l3*a2pSOO_A
# trigram_score_P ~~ l3*a2pSOO_P
# careerasp_A ~~ l4*TSO_A_SOO_P
# careerasp_P ~~ l4*TSO_P_SOO_A
# careerasp_A ~~ l5*TSO_A
# careerasp_P ~~ l5*TSO_P
# careerasp_A ~~ l6*a2pSOO_A
# careerasp_P ~~ l6*a2pSOO_P
# relag_A ~~ l7*TSO_A_SOO_P
# relag_P ~~ l7*TSO_P_SOO_A
# relag_A ~~ l8*TSO_A
# relag_P ~~ l8*TSO_P
# relag_A ~~ l9*a2pSOO_A
# relag_P ~~ l9*a2pSOO_P
# 
# #direct partner effects
# trigram_score_A ~~ m1*TSO_P_SOO_A
# trigram_score_P ~~ m1*TSO_A_SOO_P
# trigram_score_A ~~ m2*TSO_P
# trigram_score_P ~~ m2*TSO_A
# trigram_score_A ~~ m3*a2pSOO_P
# trigram_score_P ~~ m3*a2pSOO_A
# careerasp_A ~~ m4*TSO_P_SOO_A
# careerasp_P ~~ m4*TSO_A_SOO_P
# careerasp_A ~~ m5*TSO_P
# careerasp_P ~~ m5*TSO_A
# careerasp_A ~~ m6*a2pSOO_P
# careerasp_P ~~ m6*a2pSOO_A
# relag_A ~~ m7*TSO_P_SOO_A
# relag_P ~~ m7*TSO_A_SOO_P
# relag_A ~~ m8*TSO_P
# relag_P ~~ m8*TSO_A
# relag_A ~~ m9*a2pSOO_P
# relag_P ~~ m9*a2pSOO_A
# 
# #Two to four
# #direct actor effects
# trigram_score_A ~~ o1*howbody_avg_A
# trigram_score_P ~~ o1*howbody_avg_P
# careerasp_A ~~ o2*howbody_avg_A
# careerasp_P ~~ o2*howbody_avg_P
# relag_A ~~ o3*howbody_avg_A
# relag_P ~~ o3*howbody_avg_P
# 
# #direct partner effects
# trigram_score_A ~~ o1*howbody_avg_P
# trigram_score_P ~~ o1*howbody_avg_A
# careerasp_A ~~ o2*howbody_avg_P
# careerasp_P ~~ o2*howbody_avg_A
# relag_A ~~ o3*howbody_avg_P
# relag_P ~~ o3*howbody_avg_A
# 
# 
# ######covariances
# #endogenous
# howbody_avg_A ~~ howbody_avg_P
# authenticity_A ~~ authenticity_P
# #trigram_score_A ~~ trigram_score_P
# #careerasp_A ~~ careerasp_P
# #relag_A ~~ relag_P
# trigram_score_A ~~ q1*careerasp_A 
# trigram_score_A ~~ q2*relag_A
# 
# careerasp_A ~~ q3*relag_A
# 
# trigram_score_P ~~ q1*careerasp_P
# trigram_score_P ~~ q2*relag_P
# 
# careerasp_P ~~ q3*relag_P
# 
# trigram_score_A ~~ q4*careerasp_P
# trigram_score_A ~~ q5*relag_P
# 
# 
# trigram_score_P ~~ q4*careerasp_A
# trigram_score_P ~~ q5*relag_A
# 
# careerasp_A ~~ q6*relag_P
# careerasp_P ~~ q6*relag_A
# 
# 
# #####variances
# howbody_avg_A ~~ v1*howbody_avg_A
# howbody_avg_P ~~ v1*howbody_avg_P
# TSO_A ~~ v2*TSO_A
# TSO_P ~~ v2*TSO_P
# a2pSOO_A ~~ v3*a2pSOO_A
# a2pSOO_P ~~ v3*a2pSOO_P
# authenticity_A ~~ v4*authenticity_A
# authenticity_P ~~ v4*authenticity_P
# ##endogenous intercepts
# howbody_avg_A ~ i*1
# howbody_avg_P ~ i*1
# authenticity_A ~ i2*1
# authenticity_P ~ i2*1
# trigram_score_A ~ i3*1
# trigram_score_P ~ i4*1
# careerasp_A ~ i5*1
# careerasp_P ~ i5*1
# relag_A ~ i6*1
# relag_P ~ i6*1
# ##exogenous means
# TSO_A ~ m*1
# TSO_P ~ m*1
# a2pSOO_A ~ m2*1
# a2pSOO_P ~ m2*1
# TSO_P_SOO_A ~ m3*1
# TSO_A_SOO_P ~ m3*1
# ## exogenous covariances
# TSO_A_SOO_P ~~ c1*TSO_A
# TSO_P_SOO_A ~~ c1*TSO_P
# TSO_A_SOO_P ~~ c2*a2pSOO_P
# TSO_P_SOO_A ~~ c2*a2pSOO_A
# TSO_A ~~ c3*a2pSOO_P
# TSO_P ~~ c3*a2pSOO_A
# TSO_A ~~ c4*a2pSOO_A
# TSO_P ~~ c4*a2pSOO_P
# TSO_A_SOO_P ~~ c5*a2pSOO_A
# TSO_P_SOO_A ~~ c5*a2pSOO_P
# TSO_A_SOO_P ~~ c6*TSO_P
# TSO_P_SOO_A ~~ c6*TSO_A
# '
# 
# 
# 
# fit <- sem(model, data=dyad_cswomen)
# ```
# 
# ```{r sem, include=TRUE, results='asis'}
# fit_table <- xtable(parameterEstimates(fit))
# 
# fit_table <- fit_table %>%
#   filter(op=="~") %>%
#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
#   select(lhs, op, rhs, est, se, z, pvalue) %>%
#   #taking out partner-partner estimates
#   slice(1:5,11:13)
# 
# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
# 
# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
# ```
# 
# ```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
# include_graphics("SEMfigure.png")
# ```
```

>>>>

```{r data}
clark_final <- read.csv("Cleaned data/clark_final.csv")
smith_final <- read.csv("Cleaned data/smith_final.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
```

##Combined Samples

@@

Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US. The description of the samples section below contains more detail about equivalence analyses to support the decision to combine these two samples.

@@

```{r alpha_SOO}
##SOO
#Clark
clark_extsoo_alpha <- psych::alpha(select(clark_final, otherint_1, otherint_2, 
                                          otherint_5, otherint_6, otherint_10))$total[2]
clark_intsoo_alpha <- psych::alpha(select(clark_final, otherint_3, otherint_4, 
                                          otherint_7, otherint_8, otherint_9, otherint_11, 
                                          otherint_12))$total[2]
#Smith
smith_extsoo_alpha <- psych::alpha(select(smith_final, otherint_1, otherint_2, otherint_5, 
                                          otherint_6, otherint_10))$total[2]
smith_intsoo_alpha <- psych::alpha(select(smith_final, otherint_3, otherint_4, otherint_7, 
                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
```

@@

```{r alpha_intauth}
##Interaction Authenticity
#Clark
clark_intauth_alpha <- psych::alpha(select(clark_final, inter_1, inter_3, inter_5, 
                                           inter_6, inter_7, inter_9, inter_10, interaux_5, 
                                           interaux_6))$total[2]
#Smith
smith_intauth_alpha <- psych::alpha(select(smith_final, inter_1, inter_3, inter_5, inter_6, 
                                           inter_7, inter_9, inter_10, interaux_5, 
                                           interaux_6))$total[2]
```

@@

```{r alpha_SSO}
##SSO
#Clark - two items
clark_howbody_alpha<- psych::alpha(select(clark_final, howbody_1, howbody_2))$total[2]
#Smith - two items
smith_howbody_alpha <- psych::alpha(select(smith_final,  howbody_1, howbody_2))$total[2]
#Clark - three items
clark_howbody3 <- psych::alpha(select(clark_final, howbody_1, howbody_2, howbody_3))
#Smith - three items
smith_howbody3 <- psych::alpha(select(smith_final, howbody_1, howbody_2, howbody_3))
```

@@

```{r alpha_relagen}
##Relationship Agency
#Clark
clark_relag_alpha <- psych::alpha(select(clark_final, relag_1, relag_2, relag_3, 
                                         relag_4, relag_5, relag_6, relag_7, relag_8, 
                                         relag_9.r))$total[2]
#Smith
smith_relag_alpha <- psych::alpha(select(smith_final, relag_1, relag_2, relag_3, relag_4, 
                                         relag_5, relag_6, relag_7, relag_8, 
                                         relag_9.r))$total[2]

#corr.test(select(clark_final, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
#corr.test(select(smith_final, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))
##DROPPING ITEM 9
clark_relag_alpha <- psych::alpha(select(clark_final, relag_1, relag_2, relag_3, 
                                         relag_4, relag_5, relag_6, relag_7, relag_8))$total[2]

smith_relag_alpha <- psych::alpha(select(smith_final, relag_1, relag_2, relag_3, relag_4, 
                                         relag_5, relag_6, relag_7, relag_8))$total[2]
```

@@

```{r alpha_career}
##Career Aspirations
#Clark
clark_final <- clark_final %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

clark_careerasp_alpha <- psych::alpha(select(clark_final, careerasp_1, careerasp_2, 
                                             careerasp_3, careerasp4.r, careerasp_5, 
                                             careerasp_6, careerasp7.r, careerasp_8, 
                                             careerasp_9, careerasp10.r))$total[2]

#Smith
smith_final <- smith_final %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

smith_careerasp_alpha <- psych::alpha(select(smith_final, careerasp_1, careerasp_2, 
                                             careerasp_3, careerasp4.r, careerasp_5, 
                                             careerasp_6, careerasp7.r, careerasp_8, 
                                             careerasp_9, careerasp10.r))$total[2]
```

@@

```{r alpha_TSO}
###TSO
#Clark--external and internal
clark_funcTSO_alpha <- psych::alpha(select(clark_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
clark_physTSO_alpha <- psych::alpha(select(clark_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
```

@@

###Description of the Samples
Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.  More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college. Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals. Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2. For consistency, we limited participant data to same sex female pairs at the two colleges.

```{r}
##Correlations
round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Smith"), 
                 a2pSOO_A, a2pSOO_P, TSO_A,
                 howbody_avg_A,
                 authenticity_A, 
                 trigram_score_A, careerasp_A, relag_A))$r, 3)

round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Clark"), 
                 a2pSOO_A, a2pSOO_P, TSO_A, 
                 howbody_avg_A,
                 authenticity_A, 
                 trigram_score_A, careerasp_A, relag_A))$r, 3)
```

There were some similar correaltions bewtween study variables across samples.

Due these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined. These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`). The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race. There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs. The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs. `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.

@@

tally(~gender, data=clark_final)
tally(~gender, data=smith_final)
```

# Results
```{r create_r-references, warning=FALSE, message=FALSE}
#cite_r(file = "references.bib")
r_refs(file = "r-references.bib")
```
## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

@@

### Combining Samples

The correaltions between study variables is similar across samples. The realibialities for the study scales were also equivalent. (Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.

### 2020-07-06 Final_Manuscript.tex
Cleaned file i-o

Data from two different, but demographically equivalent, samples were
combined to create the final analysis sample (\emph{N =} 64) used in
this study. In the measures section that follows we refer to them as
Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
women's liberal arts college in the northeast US.

@@

>>>>

Data from two different, but demographically equivalent, samples were
combined to create the final analysis sample (\emph{N =} 64) used in
this study. In the measures section that follows we refer to them as
Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
women's liberal arts college in the northeast US. The results section
contains more detail about equivalence analyses to support the decision
to combine these two samples.

@@

Before moving to the main analyses, we discuss statistical equivalence
test that provide support for combining Sample 1 and Sample 2 in one
analysis sample. The online supplemental material contains the main
analyses separated by samples.

\subsubsection{Combining Samples}\label{combining-samples-1}

The correaltions between study variables is similar across samples. The
realibialities for the study scales were also equivalent. (Note that the
two samples were two small to conduct formal measurement equivalence
tests for scales.) There are no statistically significant differences
between samples in demographics including age, STATS, and ethnicity,
STATS.
